---
title: "covid_final"
format: html
theme: yeti
editor: visual
eval: true
echo: false
error: true
---

```{r}
#| output: false

#setting up data and library
library(usethis)
library(tidyverse)
library(dplyr)
library(gtsummary)
library(broom)
library(gt)
library(here)
#install.packages("medicaldata")
library(medicaldata)


usethis::use_git_config(user.name = "Samanta Biswas", user.email = "samantabiswas88@gmail.com")

here::i_am("covid_final.qmd")

load("covid_testing.rda")

here::here("covid_testing.rda")

here()

```

```{r}

#table of descriptive summary and labeling a table

#| label: tbl-one
#| tbl-cap: "Table 1. Descriptive stats"
covid_tab<-tbl_summary(
  covid_testing,
  by = gender,
  include = c(age, gender, result, drive_thru_ind, orderset, demo_group, payor_group, col_rec_tat, rec_ver_tat),
    label = list(
    age ~ "Age during specimen collection",
    result ~ "Covid test result",
    drive_thru_ind ~ "Collected via a drive-thru site", 
    orderset ~ "Collected via a orderset",
    demo_group ~ "Type of subject",
    payor_group ~ "Bill payor",
    col_rec_tat ~ "Time between specimen collection and lab receipt", 
    rec_ver_tat ~ "Time between lab receipt and testing"),
	missing_text = "Missing",
  statistic = list(all_continuous() ~ "{median} ({p25}, {p75})", all_categorical() ~ "{n} ({p}%)")) |>
	bold_labels() |> 
  modify_footnote(everything() ~ NA) |> 
  modify_header(label = "**Variable**")
covid_tab



# I tried adding median of the continuous variables by listing but it is showing similar values for male and female. Slso cant ssem to caption it
```

```{r}



```

```{r}

# Fitting a regression

#linear_model <- lm(ct_result ~ gender + result + drive_thru_ind + orderset + demo_group + payor_group + col_rec_tat + rec_ver_tat, 
#data = covid_testing)
#ct_reg <- tbl_uvregression(
  #covid_testing, 
  #y = ct_result,
  #include = c(gender, result, demo_group, payor_group, col_rec_tat, rec_ver_tat),
  #method = linear_model)
#Doesn't work when i try to rename the variables


```

```{r}

# Fitting a regression and labeling a table

#| label: tbl-two
#| tbl-cap: "Table 2. Regression table"
reg_tab <- tbl_regression(
  linear_model, 
  intercept = TRUE,
label = list(
    result ~ "Covid test result",
    drive_thru_ind ~ "Collected via a drive-thru site", 
    orderset ~ "Collected via a orderset",
    demo_group ~ "Type of subject",
    payor_group ~ "Bill payor",
    col_rec_tat ~ "Time between specimen collection and lab receipt", 
    rec_ver_tat ~ "Time between lab receipt and testing"))
reg_tab

# the table disappears if i try to caption it
```

```{r}

stats <- list(n = nrow(covid_testing),
              mean_age = mean(covid_testing$age))

stats


```

```{r}
# a new function - ?? object not found

 func <- function(x) {
   n <- length(x)
   total_hours <- sum (covid_testing$col_rec_tat + covid_testing$rec_ver_tat)
   return(total_hours)
 }

x <- c(covid_testing$col_rec_tat, na.rm=TRUE)
func(x)


covid_testing$covid_testing_tot<-covid_testing$col_rec_tat + covid_testing$rec_ver_tat
covid_testing$mean_hrs<-covid_testing$covid_testing_tot/2

```

```{r}
#figure with labeling

#| label: fig-one
#| fig-cap: "Fig 1. Histogram of Age"
knitr::kable(covid_testing)
hist(covid_testing$age, main="Histogram of Age", xlab="Age", col="lightblue", border="black") 


```

# Inline R text and cross-referencing:

Source: This data set is from Amrom E. Obstfeld, who de-identified data on COVID-19 testing during 2020 at CHOP (Children’s Hospital of Pennsylvania). The data has been anonymized, time-shifted, and permuted. It is from a Prospective Cross-Sectional Cohort where 15,524 participants were tested, from day 4 to day 107 of the COVID-19 pandemic. This data set contains data concerning testing for SARS-CoV2 via PCR as well as associated metadata (17 variables).

There are `r stats$n` participants with a mean age of `r stats$mean_age` or There were `r nrow(covid_testing)` participants with a mean age of `r mean(covid_testing$age)`. We plotted the histogram of age in @fig-one. However, @tbl-one shows similar median age for both men and women: `r inline_text(table1, variable = "age")`
